Recurrence spike spectra

### 2022-05-18 Manuscript/inter_spike_manuscript.tex
New figure for schema for basis functions

%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\setlength{\marginparwidth}{2cm}
\usepackage{changes}
\usepackage{bbm}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{statmath}
\usepackage[numbers]{natbib}
\usepackage{hyperref}
\usepackage{enumitem}
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Nonlinear Dynamics}
%
\begin{document}

@@

\begin{figure}
  \begin{minipage}[b]{0.3\textwidth}
    \vspace{0pt}
    \includegraphics[width=0.95\textwidth]{./figures/fig_tau_rr_basis_functions}
  \end{minipage}\hfill
  \begin{minipage}[b]{0.7\textwidth}
    \vspace{0pt}
    \caption{Example for a set of basis functions for an input signal of length $N=5$, aligned in the matrix $\bfX$.} \label{fig_tau_rr_basis_functions}
  \end{minipage}
\end{figure}

>>>>

%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\setlength{\marginparwidth}{2cm}
\usepackage{changes}
\usepackage{bbm}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{statmath}
\usepackage[numbers]{natbib}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Nonlinear Dynamics}
%
\begin{document}

@@

\begin{figure}
  \begin{minipage}[b]{0.3\textwidth}
    \vspace{0pt}
    \includegraphics[width=0.95\textwidth]{./figures/fig_tau_rr_basis_functions}
  \end{minipage}\hfill
  \begin{minipage}[b]{0.7\textwidth}
    \vspace{0pt}
    \caption{Example for a set of basis functions for an input signal of length $N=4$, aligned in the matrix $\bfX$. Inter spike periods $T_{\text{is}}$ larger 
    than $\ceil*{N/2}$ lead to redundant basis functions (i.e., repeated lines in $\bfX$, red sheared) or basis functions, which can not be uniquely assigned to a certain inter spike period 
    (blue sheared).} \label{fig_tau_rr_basis_functions}
  \end{minipage}
\end{figure}
